\begin{abstract}
This template is meant to provide an easy onboarding with \LaTeX.
We recommend using VSCode with the remote containers extensions.
Once you open this repository, you are asked to reopen in a container.

This container provides many useful features, such as
\begin{itemize}
    \item Automatic \LaTeX compilation on save.
    \item PDF Preview on the side. You can click in the PDF to find the \LaTeX source code, or you can sync our PDF view with your current Tex-File.
    \item Many useful keyboard shortcuts, e.g. for \textbf{bold} or \emph{italic} text.
    \item Automatic \textbf{grammar check} using Ltex Extension. It uses LanguageTool internally.
    \item Automatic \textbf{spell check}. You will see little yellow indicators in the editor.
    \item Many more\ldots you can provide pull requests to list your favorites features here.
\end{itemize}

How can I improve my scientific writing skills?
\begin{itemize}
 \item \url{https://www.zfw.rub.de/sz/}
 \item \url{http://www.cs.joensuu.fi/pages/whamalai/sciwri/sciwri.pdf}
 \item \url{https://www.student.unsw.edu.au/writing}
 \item \url{https://www.sydney.edu.au/content/dam/students/documents/learning-resources/learning-centre/writing-a-thesis-proposal.pdf}
\end{itemize}
\end{abstract}

\cleardoublepage

\pagestyle{scrplain} % switch off headers and footers

\section*{Eigenständigkeitserklärung}
{\selectlanguage{ngerman}
Hiermit erkläre ich, dass ich keine Arbeit in gleicher oder ähnlicher Fassung bereits als Prüfungsleistung an der Ruhr-Universität Bochum oder einer anderen Hochschule eingereicht habe.

\noindent
Ich versichere, dass die vorliegende Arbeit auf meiner konzeptionellen, methodischen und inhaltlichen Eigenleistung basiert und ich keine anderen als die angegebenen Quellen und Hilfsmittel benutzt habe. Alle direkten und indirekten Zitate sowie KI-generierten fachlichen Inhalte habe ich unter Angabe der Quellen kenntlich gemacht. Diese Versicherung bezieht sich auf alle Textbausteine, Tabellen, Codes, Grafiken und andere Abbildungen. Mir ist bewusst, dass die Unterlassung der angemessenen Dokumentation mit einem Täuschungsversuch aufgrund der Verwendung nicht zulässiger Hilfsmittel gleichzusetzen ist.

\noindent
Im Falle der Verwendung von KI-Tools habe ich allen Output sorgfältig geprüft und übernehme die volle Verantwortung für eventuell durch die KI generierte fehlerhafte oder verzerrte Inhalte, fehlerhafte Referenzen, Verstöße gegen das Datenschutz- und Urheberrecht oder Plagiate.

\noindent
Ich erkläre mich außerdem damit einverstanden, dass die digitale Version dieser Arbeit zwecks Plagiatsprüfung verwendet wird. \@}

\section*{Declaration of Authorship}
I hereby declare that I have never before submitted this paper in this or similar form for examination at Ruhr-Universität Bochum or any other institution or university.

\noindent
I profess that this paper is the result of my own conceptional, methodical and analytical work and that I have not used any sources or tools other than the ones stated.
Any quotes, whether direct or indirect, and any substantial content that was generated with the help of AI have been fully disclosed by using proper marking and quotation.
This declaration is valid for all textual elements, charts, codes, images and figures.
I am aware that neglecting the proper documentation constitutes an attempt at deception by use of unauthorized aid.

\noindent
When using AI tools, I have critically reviewed and verified all output and assume full responsibility for any misrepresented or falsified content, faulty references, plagiarism and breaches of data protection or copyright laws that may result from the use of generative AI.

\noindent
I furthermore agree that the digital version of this thesis will be used to subject the paper to plagiarism examination.

\noindent
Not this English translation but only the official version in German is legally binding.

\fbox{
 \begin{minipage}{\dimexpr\textwidth-2\fboxsep-2\fboxrule\relax}
    \begin{Form}
    Beim Verfassen dieser Arbeit habe ich die unten aufgeführten KI-Tools für folgende Zwecke verwendet:

    \noindent
    In writing this paper, I have used the AI tools specified below for the following purposes:

    \vspace{1em} % Adds vertical space

    \TextField[
    multiline=true, % Allows multiple lines of text
    height=10cm,     % Specifies the height of the box
    width=\textwidth, % Makes the box span the width of the text area
    borderstyle={solid}, % Adds a visible border
    ]{}

    \vspace{1em}
    \end{Form}
  \end{minipage}
}

\makeatletter
\vspace{2cm}
\rule{3cm}{0.1pt} \hfill \rule{6cm}{0.1pt} \hfill \rule{3cm}{0.1pt}\\
\hspace*{1cm} \textsc{Date} \hspace*{2.7cm} \textsc{\@author} \hspace*{2.2cm} \textsc{Signature}
\makeatother

\cleardoublepage

\section*{Erklärung}
{\selectlanguage{ngerman}
Ich erkläre mich damit einverstanden, dass meine Abschlussarbeit am
Lehrstuhl Netz- und Datensicherheit dauerhaft in elektronischer und gedruckter Form aufbewahrt
wird und dass die Ergebnisse aus dieser Arbeit unter Einhaltung guter
wissenschaftlicher Praxis in der Forschung weiter verwendet werden dürfen.\@}
Weiterhin erkläre ich mich damit einverstanden, dass die Abschlussarbeit auf der Webseite des Lehrstuhls bzw. des Betreuers veröffentlicht werden darf.

\makeatletter
\vspace{2cm}
\rule{3cm}{0.1pt} \hfill \rule{6cm}{0.1pt} \hfill \rule{3cm}{0.1pt}\\
\hspace*{1cm} \textsc{Date} \hspace*{2.7cm} \textsc{\@author} \hspace*{2.2cm} \textsc{Signature}
\makeatother

\cleardoublepage

\pagestyle{scrheadings} % reenable headers and footers

%% generate table of contents
\tableofcontents

\cleardoublepage
